Online learning methods for financial time series forecasting

### 2017-12-18 slides/defense-slides.tex
Adding all before the exam

\begin{frame}
\frametitle{Motivation: HFT}
\begin{alertblock}{High Frequency Trading}
High Frequency Trading (HFT) is a technology that implements different trading strategies to buy or sell an stock using sophisticated infrastructure and high speed algorithms.
\end{alertblock}
HFT challenges are related to {\bf time series forecasting} and also {\bf computational} (hardware and software). Today, the volume of data has rapidly increased:
\begin{table}
\small
\begin{tabular}{ l | c }
Period & Data precision \\
\hline \hline
1993-2003 & seconds \\
2003-2015 & milliseconds \\
27th July 2015-onwards & microseconds \\
24th October 2016-onwards & nanoseconds
\end{tabular}
\caption{High Frequency data precision}
\end{table}
\end{frame}

@@

\begin{column}{0.5\textwidth}
\begin{exampleblock}{Advantages}
\begin{itemize}
\item Increases liquidity
\item Allows more efficient price formation
\item Reduce the difference between buyers (bid) and sellers (ask) prices.
\end{itemize}
\end{exampleblock}
\end{column}
\begin{column}{0.5\textwidth}
\begin{exampleblock}{Disadvantages}
\begin{itemize}
\item Removal of human decision making could lead to failures in untested or incorrect strategies
\item fairness
\end{itemize}
\end{exampleblock}
\end{column}
\end{columns}
\end{frame}

>>>>

\begin{frame}
\frametitle{Motivation: HFT}
\begin{alertblock}{High Frequency Trading}
High Frequency Trading (HFT) is a technology that implements different trading strategies to buy or sell an asset using sophisticated infrastructure and high speed algorithms.
\end{alertblock}
HFT challenges are related to {\bf time series forecasting} and also {\bf computational} (hardware and software). Today, the volume of data has rapidly increased:
\begin{table}
\small
\begin{tabular}{ l | c }
Period & Data precision \\
\hline \hline
1993-2003 & seconds \\
2003-2015 & milliseconds \\
27th July 2015-onwards & microseconds \\
24th October 2016-onwards & nanoseconds
\end{tabular}
\caption{High Frequency data precision}
\end{table}
\end{frame}

@@

\begin{column}{0.5\textwidth}
\begin{exampleblock}{Advantages}
\begin{itemize}
\item Increases liquidity
\item Allows more efficient price formation
\item Reduces the difference between buyers (bid) and sellers (ask) prices.
\end{itemize}
\end{exampleblock}
\end{column}
\begin{column}{0.5\textwidth}
\begin{exampleblock}{Disadvantages}
\begin{itemize}
\item Removal of human decision making could lead to failures in untested or incorrect strategies
\item Fairness
\end{itemize}
\end{exampleblock}
\end{column}
\end{columns}
\end{frame}
